Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-27 draft/chicago-spatial-covid-draft.tex
Include figure and explanation of 3 waves

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=.6\textwidth]{obs_data}
	\caption{Observed data for Chicago showing the three impact waves.}
	\label{fig:obs_data}
\end{figure}

The COVID-19 pandemic had three major impact waves in Chicago, as seen clearly in Figure \ref{fig:obs_data}.
For simplicity, we analyze only the first major wave, which ends at approximately October 30, 2020.
Additionally, we begin the analysis at March 17 instead of the first day of data collection (March 1) because of reporting errors early in the pandemic.
